Generalized Tractability

### 2023-03-12 GeneralizedTractability_230310.tex
Fred M2 2023 Mac Updates

\subsection{Notation and fundamental definitions}
Let $T$ be a tractability function defined as follows,
\[
T :(0,\infty) \times \mathbb{N} \times [0,\infty)^s \rightarrow [1,\infty),
\]
A tractability function is a simple function that provides an upper bound on the computational complexity of a problem
A problem is $T$-tractable with parameter $\vp$ iff there exists a positive constant $C_{\vp}$ such that
\begin{equation} \label{eq:tract_def}
	\comp(\varepsilon,d) \le C_{\vp}\, T(\varepsilon^{-1},d,\vp) \qquad \forall \varepsilon >0, \ d \in \mathbb{N}.
\end{equation}
A problem is \emph{strongly}
$T$-tractable with parameter $\vp$ iff the complexity is independent of the dimension, that is, there exists a positive constant $C_{\vp}$ such that
\begin{equation} \label{eq:strong_tract_def}
	\comp(\varepsilon,d) \le C_{\vp}\, T(\varepsilon^{-1},1,\vp) \qquad \forall \varepsilon >0 , \ d \in \mathbb{N}.
\end{equation}

@@

If \eqref{eq:tract_def} holds for some $\vp$, it clearly holds for larger, $\vp$.  We are often interested in the optimal or smallest $\vp$ for which \eqref{eq:tract_def} holds.  Let $\cp_{\textup{true}} : = \{\vp^* : \eqref{eq:tract_def} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty})\}$
The  set of optimal parameters, $\mathcal{P}_{\text{opt}}$ is defined as
\begin{equation}
	\mathcal{P}_{\textup{opt}} : = \{\vp^* \in \cp_{\textup{true}} :  \vp* \notin [\vp^\dagger,\boldsymbol{\infty}) \ \forall \vp^\dagger \in  \cp_{\textup{true}} \setminus \{\vp^*\} \}.
\end{equation}
In this article we allow $\vp$ to be a scalar or vector as the situation requires.

Certain common notions of tractability are covered by the general situation described above
\begin{equation*}
	\begin{array}{r@{\qquad}c@{\qquad}c}
		& T(\varepsilon^{-1},d,\vp)\\
		\toprule
		\text{strong polynomial algebraic  tractability} & \max(1,\varepsilon^{-p})\\
		\text{polynomial algebraic tractability} & \max(1,\varepsilon^{-p})d^{q}\\
		\text{strong polynomial exponential tractability} &  [\max(1,\log(1 + \varepsilon^{-1})]^p\\
		\text{polynomial exponential tractability} &
		[\max(1,\log(1 + \varepsilon^{-1}))]^p  d^{q}
	\end{array}
\end{equation*}
Here, $\vp = (p,q)$ in some cases.

@@

\begin{theorem}\label{thm_main_strong_tract2}
A problem is strongly $T$-tractable iff there exists $\vp \in [\vzero, \boldsymbol{\infty})$ and an integer $L(\vp) > 0$ such that
\begin{equation} \label{eq:strong_tractiff3}
     S(p):=\sup_{d \in \naturals} \sum_{i = L(\vp)}^\infty \frac{1}{T(\lambda_{i,d}^{-1},1,\vp)} < \infty.
\end{equation}
If \eqref{eq:strong_tractiff3} holds for some $\vp$, let  $\widetilde{\cp}_{\textup{true}} : = \{\vp^* : \eqref{eq:strong_tractiff3} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty})\}$.  Then the set of optimal strong tractability parameters is
\[
	\cp_{\textup{opt}} = \widetilde{\mathcal{P}}_{\textup{opt}} :=
	\{\vp^* \in \widetilde{\cp}_{\textup{true}} :  \vp* \notin [\vp^\dagger,\boldsymbol{\infty}) \ \forall \vp^\dagger \in  \widetilde{\cp}_{\textup{true}} \setminus \{\vp^*\} \}.
\]
\end{theorem}

@@

Also since the $\lambda_{i,d}$ are non-increasing in $i$, it follows that the $T(\lambda_{i,d}^{-1},d',\vp)$ are non-decreasing in $i$. In particular, for all $n\in \mathbb{N}$, we have
\begin{align*}
    \lambda_{n+1,d} \le \lambda_{n,d} \le \cdots \le \lambda_{1,d}
    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},d',\vp)} \le \frac{1}{T(\lambda_{n, d}^{-1},d',\vp)} \le \cdots \le \frac{1}{T(\lambda_{1, d}^{-1},d',\vp)} \\
    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},d',\vp) }
    \le \frac 1n \sum_{i=1}^n  \frac{1}{T(\lambda_{i, d}^{-1},d',\vp) }
    \le \frac 1n \sum_{i=1}^\infty  \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)}.
\end{align*}
Thus, we can conclude from the previous line that
\begin{multline*}
    n \ge T(\varepsilon^{-1},d',\vp) \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)} \\
   \implies   \frac{1}{T(\lambda_{n+1, d}^{-1},d',\vp)} \le
   \frac 1n \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d',\vp) } \le \frac{1}{T(\varepsilon^{-1},d',\vp)} \qquad \forall \varepsilon > 0, \ d,d' \in \naturals.
\end{multline*}
This last inequality together with \eqref{eq:comp_equiv} implies an upper bound on the complexity: of
\begin{equation}
	\comp(\varepsilon,d)
	\le 1 + T(\varepsilon^{-1},d',\vp) \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)} \qquad \forall \varepsilon > 0, \ d, d' \in \naturals
\end{equation}

Now we take this upper bound further, specializing to the case of $d'=1$:
\begin{align*}
       \comp(\varepsilon,d)
       & = 1 + T(\varepsilon^{-1},1, \vp) \left [ \sum_{i=1}^{L(\vp)-1} \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}
       + \underbrace{\sum_{i=L(p)}^\infty \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}}_{\le S(p) <\infty\ \text{by \eqref{eq:strong_tractiff3}} }\right] \\
       & \le 1+ T(\varepsilon^{-1},1,\vp) \underbrace{\left[\frac{(L(p)-1)}{T(\lambda_{\max}^{-1},1,\vp)} + S(p)\right]}_{=:C_1(p)}\\
       & = 1+ T(\varepsilon^{-1},1,\vp) C_1 (p)\\
       &\le C_{\vp} T(\varepsilon^{-1},1,\vp),
\end{align*}
for some suitably chosen $C_{\vp}>0$. This means that we have strong $T$-tractability via \eqref{eq:strong_tract_def}, and verifies sufficiency of \eqref{eq:strong_tractiff3}.

@@

Define
\[
j (\varepsilon,\vp):= \lfloor C_{\vp}\, T(\varepsilon^{-1},1,\vp)\rfloor +1, \quad
 L(\vp):= j (\infty,\vp).
\]
Thus, it follows by \eqref{eq:lambda_K_strong3} that $\lambda_{j(\varepsilon,\vp),d} \le \varepsilon$.
Note furthermore that we always have
\[
j(\varepsilon)\le C_{\vp}\, T(\varepsilon^{-1},1,\vp)+1 \le C_{\vp} T(\lambda_{j(\varepsilon,\vp),d}^{-1},1,\vp)+1, \qquad \forall \varepsilon > 0,
\]
since
$T(\cdot,1, \vp)$ is non-decreasing.

@@

\bigskip
\noindent \textbf{Optimality:} \\
To complete the proof, we must show that $\cp_{\textup{opt}} = \widetilde{\cp}_{\textup{opt}}$.  We do this by proving that $\cp_{\textup{true}} = \widetilde{\cp}_{\textup{true}}$.  Then, since $\cp_{\textup{opt}}$ is defined in terms of $\cp_{\textup{opt}}$ in the same way as $\widetilde{\cp}_{\textup{opt}}$ is defined in terms of $\widetilde{\cp}_{\textup{opt}}$, it follows that $\cp_{\textup{opt}} = \widetilde{\cp}_{\textup{opt}}$.

If $\vp^* \in \cp_{\textup{true}}$, then \eqref{eq:strong_tract_def} holds for all $\vp \in (\vp^*,\vinfty)$.  By the argument to prove the necessary condition, it follows that \eqref{eq:strong_tractiff3} must also hold for all $\vp \in (\vp^*,\vinfty)$, so $\vp^* \in \widetilde{\cp}_{\textup{true}}$.  Conversely, if $\vp^* \in \widetilde{\cp}_{\textup{true}}$, then \eqref{eq:strong_tractiff3}  holds for all $\vp \in (\vp^*,\vinfty)$.  By the argument to prove the sufficient condition, it follows that \eqref{eq:strong_tract_def} must also hold for all $\vp \in (\vp^*,\vinfty)$, so $\vp^* \in \cp}_{\textup{true}}$.

@@

\begin{theorem}\label{thm_main_tract2}
A problem is $T$-tractable iff there exist $p,q>0$, and $q_1>0$ and a constant $L(p,q_1) > 0$ such that
\begin{equation} \label{eq:tractiff4}
     S_{p,q,q_1}:=\sup_{d \in \naturals}
     \sum_{i = \lceil L(p,q_1)\, T(0,d,p,q_1) \rceil}^\infty \frac{1}{T(\lambda^{-1}_{i,d},d,p,q)}< \infty.
\end{equation}
\end{theorem}

\peter{(PETER: Do we also want to include a statement on the optimal parameters $p^*,q^*$?)}

\begin{proof}
    \textbf{Sufficient Condition:}\\ Suppose that \eqref{eq:tractiff4} holds for some $p,q>0$.
Because $T$ is increasing in its arguments, it follows that the complexity may be equivalently expressed as
\begin{align*}
    \comp(\varepsilon, d) &= \min \{n \in \natzero : \lambda_{n+1, d} \le \varepsilon\} \\
    &= \min \biggl\{n \in \natzero : \frac{1}{T(\lambda_{n+1, d}^{-1},d,p,q)} \le \frac{1}{T(\varepsilon^{-1},d,p,q)} \biggr\}.
\end{align*}

Since the $\lambda_{i,d}$ are non-increasing it follows that the $\phi(\lambda_{i, d}^{-1},p)$ are non-decreasing.
In particular, for all $n \in \naturals$,
\begin{align*}
    \MoveEqLeft{\lambda_{n+1,d} \le \lambda_{n,d} \le \cdots \le \lambda_{1,d}} \\
    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},d,p,q)} \le \frac{1}{T(\lambda_{n, d}^{-1},d,p,q))} \le \cdots \le \frac{1}{T(\lambda_{1, d}^{-1},d,p,q)} \\
    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},d,p.q)}
    \le \frac 1n \sum_{i=1}^n  \frac{1}{T(\lambda_{i, d}^{-1},d,p,q)}
    \le \frac 1n \sum_{i=1}^\infty  \frac{1}{T(\lambda_{i, d}^{-1},d,p,q)}.
\end{align*}
Thus, we can conclude that
\begin{align*}
    n \ge T(\varepsilon^{-1},d,p,q) \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d,p,q)}
    & \implies
  \frac 1n \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d,p,q)} \le  \frac{1}{T(\varepsilon^{-1},d,p,q)} \\
   & \implies   \frac{1}{T(\lambda_{n+1, d}^{-1},d,p,q)} \le \frac{1}{T(\varepsilon^{-1},d,p,q)}.
\end{align*}
This implies an upper bound on the complexity of
\begin{align*}
       \MoveEqLeft{\comp(\varepsilon,d)} \\
       &\le 1 + T(\varepsilon^{-1},d,p,q) \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d,p,q)} \\
       & = 1 + T(\varepsilon^{-1},d,p,q) \left [ \sum_{i=1}^{\lceil L(p,q_1)\, T(0,d,p,q_1)\rceil -1} \frac{1}{T(\lambda_{i, d}^{-1},d,p,q)}
       + \sum_{i=\lceil L(p,q_1)\, T(0,d,p,q_1) \rceil}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d,p,q)} \right ] \\
       & \le 1+ T(\varepsilon^{-1},d,p,q)\left[ \frac{\lceil L(p,q_1)\, T(0,d,p,q_1)\rceil-1}{T(\lambda_{\max}^{-1},d,p,q)} + S_{p,q,q_1}\right]
        \qquad \text{by \eqref{eq:tractiff4}} \\
       & \le 1+ T(\varepsilon^{-1},d,p,q)\left[L(p,q_1)\, T(0,d,p,q_1) + S_{p,q,q_1}\right]\\
       & \le 1+L(p,q_1)\,T(\varepsilon^{-1},d,p,q) T(0,d,p,q_1) + S_{p,q,q_1}\, T(\varepsilon^{-1},d,p,q)\\
       & \le 1+L(p,q_1)\,T(\varepsilon^{-1},d,p,q) T(\varepsilon^{-1},d,p,q_1) + S_{p,q,q_1}\, T(\varepsilon^{-1},d,p,q)\\
       & \le 1+L(p,q_1)\,T(\varepsilon^{-1},d,2p,2\max\{q,q_1\})  + S_{p,q}\, T(\varepsilon^{-1},d,p,q)  \\
       & \le C_{2p,2\max\{q,q_1\}} \,T(\varepsilon^{-1},d,2p,2\max\{q,q_1\})
\end{align*}
for some suitably chosen $C_{2p,2\max\{q,q_1\}}>0$. It follows that we have $T$-tractability, which shows sufficiency of \eqref{eq:tractiff4}. \\

\textbf{Necessary condition:}\\
Suppose that we have
$T$-tractability. That is, for some $p>0$ and $q>0$, there exists a positive constant $C_{p,q}$ such that
\[
\comp(\varepsilon,d)\le C_{p,q}\, (T(\varepsilon^{-1},d,p,q)
\]
for all $\varepsilon\in (0,\infty)$ and all $d\in\naturals$.

We know that
\[
\lambda_{\comp(\varepsilon,d)+1,d}\le \varepsilon.
\]
Since the eigenvalues $\lambda_{j,d}$ are non-increasing, we have
\begin{equation}\label{eq:lambda_K4}
\lambda_{\lfloor C_{p,q}\, T(\varepsilon^{-1},d,p,q)\rfloor +1,d}\le \varepsilon.
\end{equation}
Let
\[
j=j (\varepsilon):= \lfloor C_{p,q}\, T(\varepsilon^{-1},d,p,q)\rfloor +1.
\]
If we vary $\varepsilon\in (0,\infty)$, we see that $j=j_d^*, j_d^*+1, j_d^*+2,\ldots$, where
\[
  j_d^*=\lfloor C_{p,q}\, T(0,d,p,q)\rfloor +1
\]
Note that
\[
j\le C_{p,q}\, T(\varepsilon^{-1},d,p,q) +1.
\]
Due to our assumptions, we know that
$T(\cdot,d,p,q)$ is increasing in the first argument if
we keep $p$ and $q$ fixed.

Then, by \eqref{eq:lambda_K4},
\[
j \le C_{p,q}\, T(\varepsilon^{-1},d,p,q) +1 \le C_{p,q}\, T(\lambda_{j,d}^{-1},d,p,q) +1,
\]
and the latter chain of inequalities holds for all $j\ge j_d^*$.

>>>>

\subsection{Notation and fundamental definitions}
Let $T$ be a tractability function defined as follows,
\[
T :(0,\infty) \times \mathbb{N} \times [0,\infty)^s \rightarrow [1,\infty),
\]
A tractability function is a simple function that provides an upper bound on the computational complexity of a problem
A problem is $T$-tractable with parameter $\vp$ iff there exists a positive constant $C_{\vp}$ such that
\begin{equation} \label{eq:tract_def}
	\comp(\varepsilon,d) \le C_{\vp}\, T(\varepsilon^{-1},d,\vp) \qquad \forall \varepsilon >0, \ d \in \mathbb{N}.
\end{equation}
A problem is \emph{strongly}
$T$-tractable with parameter $\vp$ iff the complexity is independent of the dimension, that is, there exists a positive constant $C_{\vp}$ such that
\begin{equation} \label{eq:strong_tract_def}
	\comp(\varepsilon,d) \le C_{\vp}\, T(\varepsilon^{-1},1,\vp) \qquad \forall \varepsilon >0 , \ d \in \mathbb{N}.
\end{equation}
In this article we allow $\vp$ to be a scalar or vector as the situation requires.

@@

If \eqref{eq:tract_def} holds for some $\vp$, it clearly holds for larger, $\vp$.  We are often interested in the optimal or smallest $\vp$ for which \eqref{eq:tract_def} holds.  Let
\begin{equation*}
	\cp_{\textup{trct}} : = \{\vp^* : \eqref{eq:tract_def} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty})\}, \qquad
	\cp_{\textup{strct}} : = \{\vp^* : \eqref{eq:strong_tract_def} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty})\}.
\end{equation*}
The  set of optimal parameters is defined as all of those parameters satisfying the (strong) tractability conditions that are not greater than or equal to others:
\begin{gather}
	\label{eq:Poptdef}
	\mathcal{P}_{\textup{opt}} : = \{\vp^* \in \cp_{\textup{trct}} :  \vp* \notin [\vp^\dagger,\boldsymbol{\infty}) \ \forall \vp^\dagger \in  \cp_{\textup{trct}} \setminus \{\vp^*\} \}, \\
	\label{eq:Psoptdef}
	\mathcal{P}_{\textup{sopt}} : = \{\vp^* \in \cp_{\textup{strct}} :  \vp* \notin [\vp^\dagger,\boldsymbol{\infty}) \ \forall \vp^\dagger \in  \cp_{\textup{strct}} \setminus \{\vp^*\} \}.
\end{gather}

Certain common notions of tractability are covered by the general situation described above
\begin{equation*}
	\begin{array}{r@{\qquad}c@{\qquad}cc}
		& T(\varepsilon^{-1},d,\vp)
		& T(0,d,\vp)\\
		\toprule
		\text{strong polynomial algebraic  tractability} & \max(1,\varepsilon^{-p}) & 1\\
		\text{polynomial algebraic tractability} & \max(1,\varepsilon^{-p})d^{q} & d^{q}\\
		\text{strong polynomial exponential tractability} &  [\max(1,\log(1 + \varepsilon^{-1})]^p & 1\\
		\text{polynomial exponential tractability} &
		[\max(1,\log(1 + \varepsilon^{-1}))]^p  d^{q} & d^{q}
	\end{array}
\end{equation*}
Here above, $\vp = (p,q)$ in some cases.

@@

\begin{theorem}\label{thm_main_strong_tract2}
A problem is strongly $T$-tractable iff there exists $\vp \in [\vzero, \boldsymbol{\infty})$ and an integer $L(\vp) > 0$ such that
\begin{equation} \label{eq:strong_tractiff3}
     S(\vp):=\sup_{d \in \naturals} \sum_{i = L(\vp)}^\infty \frac{1}{T(\lambda_{i,d}^{-1},1,\vp)} < \infty.
\end{equation}
If \eqref{eq:strong_tractiff3} holds for some $\vp$, let  $\widetilde{\cp}_{\textup{strct}} : = \{\vp^* : \eqref{eq:strong_tractiff3} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty})\}$.  Then $\cp_{\textup{strct}} = \widetilde{\cp}_{\textup{strct}}$, and the set of optimal strong tractability parameters is
\[
	\cp_{\textup{sopt}} =
	\{\vp^* \in \widetilde{\cp}_{\textup{strct}} :  \vp* \notin [\vp^\dagger,\boldsymbol{\infty}) \ \forall \vp^\dagger \in  \widetilde{\cp}_{\textup{strct}} \setminus \{\vp^*\} \}.
\]
\end{theorem}

@@

Also since the $\lambda_{i,d}$ are non-increasing in $i$, it follows that the $T(\lambda_{i,d}^{-1},d',\vp)$ are non-decreasing in $i$. In particular, for all $n\in \mathbb{N}$, we have
\begin{align*}
    \lambda_{n+1,d} \le \lambda_{n,d} \le \cdots \le \lambda_{1,d}
    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},d',\vp)} \le \frac{1}{T(\lambda_{n, d}^{-1},d',\vp)} \le \cdots \le \frac{1}{T(\lambda_{1, d}^{-1},d',\vp)} \\
    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},d',\vp) }
    \le \frac 1n \sum_{i=1}^n  \frac{1}{T(\lambda_{i, d}^{-1},d',\vp) }
    \le \frac 1n \sum_{i=1}^\infty  \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)}.
\end{align*}
Thus, we can conclude from the previous line that
\begin{multline*}
    n \ge T(\varepsilon^{-1},d',\vp) \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)} \\
   \implies   \frac{1}{T(\lambda_{n+1, d}^{-1},d',\vp)} \le
   \frac 1n \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d',\vp) } \le \frac{1}{T(\varepsilon^{-1},d',\vp)} \qquad \forall \varepsilon > 0, \ d,d' \in \naturals.
\end{multline*}
This last inequality together with \eqref{eq:comp_equiv} implies an upper bound on the complexity: of
\begin{equation} \label{eq:compUP}
	\comp(\varepsilon,d)
	\le 1 + T(\varepsilon^{-1},d',\vp) \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)} \qquad \forall \varepsilon > 0, \ d, d' \in \naturals
\end{equation}

Now we take this upper bound further, specializing to the case of $d'=1$:
\begin{align*}
       \comp(\varepsilon,d)
       & = 1 + T(\varepsilon^{-1},1, \vp) \left [ \sum_{i=1}^{L(\vp)-1} \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}
       + \underbrace{\sum_{i=L(p)}^\infty \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}}_{\le S(p) <\infty\ \text{by \eqref{eq:strong_tractiff3}} }\right] \\
       & \le 1+ T(\varepsilon^{-1},1,\vp) \underbrace{\left[\frac{(L(p)-1)}{T(\lambda_{\max}^{-1},1,\vp)} + S(\vp)\right]}_{=:C_1(\vp)}\\
       & = 1+ T(\varepsilon^{-1},1,\vp) C_1 (p)\\
       &\le C_{\vp} T(\varepsilon^{-1},1,\vp),
\end{align*}
for some suitably chosen $C_{\vp}>0$. This means that we have strong $T$-tractability via \eqref{eq:strong_tract_def}, and verifies sufficiency of \eqref{eq:strong_tractiff3}.

@@

Define
\[
j (\varepsilon,\vp):= \lfloor C_{\vp}\, T(\varepsilon^{-1},1,\vp)\rfloor +1, \quad
 L(\vp):= j (\infty,\vp).
\]
Thus, it follows by \eqref{eq:lambda_K_strong3} that $\lambda_{j(\varepsilon,\vp),d} \le \varepsilon$.
Note furthermore that we always have
\[
j(\varepsilon,\vp)\le C_{\vp}\, T(\varepsilon^{-1},1,\vp)+1 \le C_{\vp} T(\lambda_{j(\varepsilon,\vp),d}^{-1},1,\vp)+1, \qquad \forall \varepsilon > 0,
\]
since
$T(\cdot,1, \vp)$ is non-decreasing.

@@

\bigskip
\noindent \textbf{Optimality:} \\
To complete the proof, we must show that $\cp_{\textup{strct}} = \widetilde{\cp}_{\textup{strct}}$.  Then, the expression for  $\cp_{\textup{sopt}}$ automatically follows from its definition in \eqref{eq:Psoptdef}.

If $\vp^* \in \cp_{\textup{strct}}$, then \eqref{eq:strong_tract_def} holds for all $\vp \in (\vp^*,\vinfty)$.  By the argument to prove the necessary condition, it follows that \eqref{eq:strong_tractiff3} must also hold for all $\vp \in (\vp^*,\vinfty)$, so $\vp^* \in \widetilde{\cp}_{\textup{strct}}$.  Conversely, if $\vp^* \in \widetilde{\cp}_{\textup{strct}}$, then \eqref{eq:strong_tractiff3}  holds for all $\vp \in (\vp^*,\vinfty)$.  By the argument to prove the sufficient condition, it follows that \eqref{eq:strong_tract_def} must also hold for all $\vp \in (\vp^*,\vinfty)$, so $\vp^* \in \cp}_{\textup{strct}}$.

@@

\begin{theorem}\label{thm_main_tract2}
A problem is $T$-tractable iff there exist $\vp\ge \vzero$ and a constant $L(\vp) > 0$ such that
\begin{equation} \label{eq:tractiff4}
     S(\vp):=\sup_{d \in \naturals}
     \sum_{i = \lceil L(\vp)\, T(0,d,\vp) \rceil}^\infty \frac{1}{T(\lambda^{-1}_{i,d},d,\vp)}< \infty.
\end{equation}
If \eqref{eq:tractiff4} holds for some $\vp$, let  $\widetilde{\cp}_{\textup{trct}} : = \{\vp^* : \eqref{eq:tractiff4} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty})\}$.  Then $\cp_{\textup{trct}} = \widetilde{\cp}_{\textup{trct}}$, and the set of optimal strong tractability parameters is
\[
\cp_{\textup{opt}} =
\{\vp^* \in \widetilde{\cp}_{\textup{trct}} :  \vp* \notin [\vp^\dagger,\boldsymbol{\infty}) \ \forall \vp^\dagger \in  \widetilde{\cp}_{\textup{trct}} \setminus \{\vp^*\} \}.
\]\end{theorem}

\begin{proof}
    \textbf{Sufficient Condition:}\\
Suppose that \eqref{eq:tractiff4} holds for some $\vp \ge 0$. By the argument in the proof of the sufficient condition for Theorem \ref{thm_main_strong_tract2}, it follows from \eqref{eq:compUP} with $d'=d$ that the complexity has an upper bound of
\begin{equation*}
	 \comp(\varepsilon,d)} \le 1 + T(\varepsilon^{-1},d,\vp) \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}
\end{equation*}

Let $J(\vp,d): = \lceil L(\vp)\, T(0,d,\vp)\rceil$.  Then this upper bound on the complexity can be further bounded above by
\begin{align*}
       \comp(\varepsilon,d)
       & = 1 + T(\varepsilon^{-1},d,\vp) \Biggl [ \sum_{i=1}^{J(\vp,d) -1} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}
       + \underbrace{\sum_{i=J(\vp,d)}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}}_{\le S(\vp) \text{ by \eqref{eq:tractiff4}}} \Biggr ] \\
       & \le 1+ T(\varepsilon^{-1},d,\vp)\left[ \frac{J(\vp,d)-1}{T(\lambda_{\max}^{-1},d,\vp)} + S(\vp)\right]
        \\
       & \le 1+ T(\varepsilon^{-1},d,\vp)\left[L(\vp)\, T(0,d,\vp) + S(\vp)\right] \qquad \text{since } T(\lambda_{\max}^{-1},d,\vp) \ge 1\\
       & \le 1+L(\vp)\,T(\varepsilon^{-1},d,\vp) T(0,d,\vp) + S(\vp)\, T(\varepsilon^{-1},d,\vp)\\
       & \le 1+L(\vp)\,T(\varepsilon^{-1},d,\vp) T(\varepsilon^{-1},d,\vp) + S(\vp)\, T(\varepsilon^{-1},d,\vp)\\
       & \le 1+L(\vp)\,K_{\vp,2} T(\varepsilon^{-1},d,2\vp)  + S(\vp)\, T(\varepsilon^{-1},d,\vp)  \qquad \text{by \eqref{eq:ptauassume}}\\
       & \le C_{2}(2\vp) \,T(\varepsilon^{-1},d,2\vp)
\end{align*}
for some suitably chosen $C_{2}(2\vp)>0$. It follows that we have $T$-tractability, which shows sufficiency of \eqref{eq:tractiff4}. \\

\noindent \textbf{Necessary condition:}\\
Suppose that we have
$T$-tractability. That is, for some $\vp \ge \vzero$, there exists a positive constant $C_{\vp}$ such that
\[
\comp(\varepsilon,d)\le C_{\vp}\, (T(\varepsilon^{-1},d,\vp) \qquad \forall \varepsilon > 0,  \ d \in \naturals.
\]
Since the eigenvalues $\lambda_{j,d}$ are non-increasing, we have
\begin{equation}\label{eq:lambda_K4}
	\lambda_{\lfloor C_{\vp}\, T(\varepsilon^{-1},d,\vp)\rfloor +1,d}\le \varepsilon.
\end{equation}
Define
\[
j (\varepsilon,d,\vp):= \lfloor C_{\vp}\, T(\varepsilon^{-1},d,\vp)\rfloor +1, \quad
j (\infty,d,\vp) = \lfloor C_{\vp}\, T(0,d,\vp)\rfloor +1.
\]
Thus, it follows by \eqref{eq:lambda_K4} that $\lambda_{j(\varepsilon,d,\vp),d} \le \varepsilon$.
Note furthermore that we always have
\[
j(\varepsilon,d,\vp)\le C_{\vp}\, T(\varepsilon^{-1},1,\vp)+1 \le C_{\vp} T(\lambda_{j(\varepsilon,d,\vp),d}^{-1},1,\vp)+1, \qquad \forall \varepsilon > 0, \ d \in \naturals
\]
since
$T(\cdot,d,\vp)$ is non-decreasing.

For $\varepsilon$ taking on all positive values, $j(\varepsilon,d,\vp)$ takes on all values greater than or equal to $j(\infty,d,\vp)$, so
\[
j\le C_{\vp}\, T(\varepsilon^{-1},d,\vp)+1 \le C_{\vp} T(\lambda_{j,d}^{-1},d,\vp)+1, \qquad \forall j \ge j(\infty,d,\vp).
\]
This implies via our technical assumption \eqref{eq:ptauassume} that
\begin{equation*}
	K_{\vp,\tau}\,T (\lambda_{j,d}^{-1},1,\tau \vp) \ge
	[T(\lambda_{j,d}^{-1},1, \vp)]^\tau
	\ge
	\left[\frac{(j-1)}{C_{\vp}}\right]^\tau \qquad \forall j \ge j(\infty,d,\vp)
\end{equation*}
Summing both sides of the inequality yields and noting that $L(\vp) \le L(\tau\vp)$, it follows that
\begin{multline*}
	\sup_{d\in\naturals} \sum_{j=L(\tau\vp)}^\infty \frac{1}{T (\lambda_{j,d}^{-1},1, \tau \vp)} \le
	\sup_{d\in\naturals} \sum_{j=L(\vp)}^\infty \frac{1}{T (\lambda_{j,d}^{-1},1, \tau \vp)} \\
	\le K_{\vp,\tau}\, C_{\vp}^\tau
	\sum_{j=L(\vp)}^\infty \frac{1}{(j-1)^\tau} \le
	K_{\vp,\tau}\, C_{\vp}^\tau\, \zeta (\tau) < \infty,
\end{multline*}
where $\zeta$ denotes the Riemann zeta function.
This yields \eqref{eq:strong_tractiff3} with $p$ replaced by $\tau p$, and so we see the necessity of $\eqref{eq:strong_tractiff3}$.

We know that
\[
\lambda_{\comp(\varepsilon,d)+1,d}\le \varepsilon.
\]
Since the eigenvalues $\lambda_{j,d}$ are non-increasing, we have
\begin{equation}\label{eq:lambda_K4}
\lambda_{\lfloor C_{\vp}\, T(\varepsilon^{-1},d,\vp)\rfloor +1,d}\le \varepsilon.
\end{equation}
Let
\[
j=j (\varepsilon):= \lfloor C_{\vp}\, T(\varepsilon^{-1},d,\vp)\rfloor +1.
\]
If we vary $\varepsilon\in (0,\infty)$, we see that $j=j_d^*, j_d^*+1, j_d^*+2,\ldots$, where
\[
  j_d^*=\lfloor C_{\vp}\, T(0,d,\vp)\rfloor +1
\]
Note that
\[
j\le C_{\vp}\, T(\varepsilon^{-1},d,\vp) +1.
\]
Due to our assumptions, we know that
$T(\cdot,d,\vp)$ is increasing in the first argument if
we keep $p$ and $q$ fixed.

Then, by \eqref{eq:lambda_K4},
\[
j \le C_{\vp}\, T(\varepsilon^{-1},d,\vp) +1 \le C_{\vp}\, T(\lambda_{j,d}^{-1},d,\vp) +1,
\]
and the latter chain of inequalities holds for all $j\ge j_d^*$.

This implies
\[
T(\lambda_{j,d}^{-1},d, \vp) \ge \frac{j-1}{C_{\vp}}.
\]
This, in turn, implies, for any $\tau>1$, that
\[
 (T(\lambda_{j,d}^{-1},d,\vp))^\tau \ge \frac{(j-1)^\tau}{C_{\vp}^\tau},
\]
which yields
\[
 K_{\vp,\tau}\, T (\lambda_{j,d}^{-1},d,\tau p,\tau q) \ge (T(\lambda_{j,d}^{-1},d, \vp))^\tau
 \ge \frac{(j-1)^\tau}{C_{\vp}^\tau}.
\]
This then implies
\[
\sum_{j=j_d^*}^\infty \frac{1}{T(\lambda_{j,d}^{-1},d, \tau p,\tau q)}
\le K_{\vp,\tau}\, C_{\vp}^\tau \sum_{j=j_d^*}^\infty \frac{1}{(j-1)^\tau}
\peter{\le K_{\vp,\tau}\, C_{\vp}^\tau \, \zeta(\tau)}
<\infty.
\]
\peter{
Consequently,
\[
\sup_{d\in\naturals} \sum_{j=j_d^*}^\infty \frac{1}{T(\lambda_{j,d}^{-1},d, \tau p,\tau q)} \le K_{\vp,\tau}\, C_{\vp}^\tau \, \zeta(\tau) < \infty.
\]
}
Note now that, \peter{for any $d\in\naturals$,}
\[
 j_d^* = \lfloor C_{\vp}\, T(0,d,\vp)\rfloor +1 \le \lfloor C_{\vp}^\tau\, T(0,d,\tau p,\tau q)\rfloor +1.
\]
So, there exists $L(\tau p,\tau q)$ such that
\[
\peter{\sup_{d\in\naturals}}\,\, \sum_{j=\lceil L(\tau p,\tau q) T(0,d,\tau p,\tau q)\rceil}^\infty \frac{1}{T(\lambda_{j,d}^{-1},d, \tau p,\tau q)}<\infty.
\]
